---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# MadagascarWeatherStations

<!-- badges: start -->
<!-- badges: end -->

The MadagascarWeatherStations package provides tools for
fetching, processing, and analyzing weather data in the South West of Madagascar.
This includes the following data sources:

1. Ambient Weather Sensors, whose data is collected via the Ambient Weather API,
2. Indoor Sensors, whose data is collected via manual downloads from the HOBO app, and
3. AirQO Sensors, whose data is collected via the AirQO API (TBD)

It includes functions for retrieving data from the sources, cleaning and merging datasets,
and storing the processed data in a standardized format for further analysis.

## Installation

You can install the development version of MadagascarWeatherStations like so:

``` r
# install.packages("devtools")
devtools::install_github("GoldenPlanetaryHealthLab/MadagascarWeatherStations")
```

## Pipeline Implementation

The pipeline is implemented in two main functionalities:

1. `targets` pipeline: This is the core of the data processing
 workflow, which defines a series of targets that represent different stages
 of the data processing. Each target is responsible for a specific task, 
 such as fetching data, cleaning it, or saving it to disk. The `targets` 
 package manages the dependencies between these targets (as a DAG) and 
 ensures that they are executed in the correct order.

2. `maestro` scheduling: This is responsible for scheduling the
 execution of the `targets` pipeline. While `targets` is defined
 for static pipelines, `maestro` allows us to specify how
  often we want the pipeline to update local data (e.g., every hour, daily, etc.) 
  and handles the execution of the pipeline according to that schedule.

See vignette("pipeline-definition") for more details on how the pipeline is defined and implemented.

## Accessing the Data

Once you've installed the package, you must first run
the `targets` pipeline to fetch and process it locally to your
project. To do this, you must first access an API key for the
Ambient Weather API, and set it in your `.Renviron` file. 
See [here](https://github.com/andrewflack/ambientweatheR)[^1] for more information on that. Then, you can run the pipeline
by executing `tar_make()` in the R console. This will execute all defined
targets, processing the data and generating clean datasets.

[^1]: Note: the `ambientweatheR` package is a 
dependency of this package, but I found a bug in
it that I fixed in [this pull request](https://github.com/andrewflack/ambientweatheR/pull/3).

Once the `targets` pipeline has run, access the datasets by:

```{r}
library(MadagascarWeatherStations)
library(dplyr) # for pipe and glimpse()
library(targets)

# Load the indoor data
indoor_data <- tar_read(indoor_sensor_database)

# Load the ambient weather station data
# note that these are parquet files, not data frames;
# we store them this way to avoid duplicating data in memory
# and to allow for more efficient storage and retrieval of large datasets
ambient_data <- tar_read(ambient_weather_station_database) %>%
  purrr::map(nanoparquet::read_parquet) %>%
  purrr::list_rbind()

# Load the AirQO data (TBD)
```

```{r}
glimpse(indoor_data)
```

```{r}
glimpse(ambient_data)
```


