---
title: "flat_clean_and_merge_indoor.Rmd empty"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r development, include=FALSE}
library(testthat)
```

```{r development-load}
# Load already included functions if relevant
pkgload::load_all(export_all = FALSE)
```

This notebook develops a simple function that is the main data processing function in the pipeline for indoor
data. It takes raw data from the "data/" directory, cleans it, and merges it into a single dataset 
that can be used for analysis and visualization.

First, we must check that all of the files we receive are uniform and consistent.


```{r}
library(targets)
library(dplyr)
library(readxl)
library(stringr)
library(janitor)
library(lubridate)
library(here)
```

Reading in the data from the targets pipeline:

```{r}
raw_data_files <- tar_read(raw_data_files, store = here("_targets")) %>%
  str_subset("Logger")

raw_data_files
```

We can test out reading in one of these files:

```{r}
dat <- read_xlsx(raw_data_files[[1]])
dat
```

This looks great so far. We can skip the first column
and clean up the column names:

```{r}
dat <- read_xlsx(raw_data_files[[1]]) %>%
  clean_names() %>%
  select(-1)

dat
```

Date is in EAT time zone, so we should
create a local date column and a GMT column:

```{r}
eat <- "Indian/Antananarivo"

dat <- read_xlsx(raw_data_files[[1]]) %>%
  clean_names() %>%
  select(-1) %>%
  rename(local_date = date_time_eat) %>%
  mutate(local_date = with_tz(local_date, tzone = eat),
         gmt_date = with_tz(local_date, tzone = "GMT"))

dat
```

I don't like the RH, so we rename manually to relative humidity:

```{r}
dat <- dat %>%
  rename(rel_humidity_percent = rh_percent)
dat
```

There are other sheets to explore:

```{r}
sheets <- excel_sheets(raw_data_files[[1]])

all_dat <- lapply(sheets, function(x) {
  print(x)
  read_xlsx(raw_data_files[[1]], sheet = x)
})
```

We have an events and details sheet,
but it looks like the data itself is in the Data sheet.

We can use the events sheet to check on the metadata,
such as the device on and off times in case of any weird  data:

```{r}
all_dat[[2]]
```

The details sheet just tells us about the device itself,
which may come in handy if we have to do some extra
checks:

```{r}
all_dat[[3]]
```

Note that this also tells us the logging frequency (every 5 minutes)
and different settings of the device itself. Not particularly useful
at the moment, but good to know.

# clean_and_merge_indoor

```{r development-clean_and_merge_indoor}
# Prepare the code of your function here
```

```{r function-clean_and_merge_indoor}
#' clean_and_merge_indoor Title
#'
#' @importFrom readxl read_xlsx
#' @importFrom janitor clean_names
#' @importFrom dplyr rename select mutate full_join arrange
#' @importFrom tidyr fill
#' @importFrom purrr map_dfr
#' @importFrom lubridate with_tz
#' @return tibble
#' @export
#'
clean_and_merge_indoor <- function(raw_data_file, sh_name = "Data", eat = "Indian/Antananarivo") {

  data <- raw_data_file %>%
    read_xlsx(sheet = sh_name) %>%
    clean_names() %>%
    select(-1) %>%
    rename(local_date = date_time_eat) %>%
    mutate(local_date = with_tz(local_date, tzone = eat),
          gmt_date = with_tz(local_date, tzone = "GMT")) %>%
    rename(rel_humidity_percent = rh_percent)
  
  logger_events <- raw_data_file %>%
    read_xlsx(sheet = "Events") %>%
    clean_names() %>%
    rename(local_date = date_time_eat, logging_period = number) %>%
    mutate(local_date = with_tz(local_date, tzone = eat))

  #expand the events to match the full date range of data

  data_clean <- logger_events %>%
    full_join(data) %>%
    arrange(local_date) %>%
    fill(logging_period, .direction = "down")

  data_clean
}
```

```{r tests-clean_and_merge_indoor}
test_that("clean_and_merge_indoor works", {
  expect_true(inherits(clean_and_merge_indoor, "function"))
})
```


```{r development-inflate, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(flat_file = "dev/flat_clean_and_merge_indoor.Rmd", vignette_name = "Clean and Merge Indoor Data", check=FALSE, open=FALSE, clean=TRUE)
```

